A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-10-07 latex/main.tex
Updates from Overleaf

\begin{table}
\centering
\caption{
Sc2ts detection results for Pango X lineages not added to the ARG.
Some Pango X lineages present in the Viridian v04 dataset
were not integrated into the ARG absent in the ARG.
The number of samples in Viridian v04 dataset
assigned to a Pango X lineage and
the number of samples which passed sequence-level quality control
are shown here.
}
\label{tab:absent_pango_x}
\begin{tabular}{crrr}
\toprule
Pango & Samples in Viridian & Samples passing QC & Breakpoints \\
\midrule
XBJ & 2 & 1 & 1\\
XBP & 8 & 2 & 1\\
XBS & 19 & 15 & 1\\
XBW & 1 & 1 & 1\\
XCA & 11 & 4 & 1\\
XAK & 2 & 2 & 1\\   % Multiple breakpoint Pango X
XAY & 15 & 11 & 6\\ % Multiple breakpoint Pango X
XBC & 36 & 21 & 3\\ % Multiple breakpoint Pango X
XBL & 2 & 2 & 0\\   % Multiple breakpoint Pango X
XBT & 1 & 1 & 2\\   % Multiple breakpoint Pango X
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption{
Sc2ts detection results for Pango X lineages not added to the ARG.
Some Pango X lineages present in the Viridian v04 dataset
were not integrated into the ARG due to high HMM costs
The number of samples in Viridian v04 dataset
assigned to a Pango X lineage and
the number of samples which passed sequence-level quality control
are shown here.
}
\label{tab:absent_pango_x}
\begin{tabular}{crrr}
\toprule
Pango & Samples in Viridian & Samples passing QC & Breakpoints \\
\midrule
XBJ & 2 & 1 & 1\\
XBP & 8 & 2 & 1\\
XBS & 19 & 15 & 1\\
XBW & 1 & 1 & 1\\
XCA & 11 & 4 & 1\\
XAK & 2 & 2 & 1\\   % Multiple breakpoint Pango X
XAY & 15 & 11 & 6\\ % Multiple breakpoint Pango X
XBC & 36 & 21 & 3\\ % Multiple breakpoint Pango X
XBL & 2 & 2 & 0\\   % Multiple breakpoint Pango X
XBT & 1 & 1 & 2\\   % Multiple breakpoint Pango X
\bottomrule
\end{tabular}
\end{table}
